---
title: "Week 4 Practical"
author: "Tiffany Wheeler"
date: "2025-10-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Creating some instructions

When you use a # it serves as a comment just for you. 

When you want to assign a variable then use <-

When you want to create a vector use c(). For example my_name <- c("Tiffany", "Wheeler")

If I want to name that vector then use names(my_name) <- c("First", "Last")

To create a matrix {which is used for a collection of elemnts of the same data type} 

```{r name}
my_name <- c("Tiffany", "Wheeler")
names(my_name) <- c("First", "Last")
my_name["First"]
```
## Some additional code

```{r grade types}
Mark_Types <- c(A = "excellent", B = "very good", c = "good")
Mark_Types
```
## Here are some lists 

- [ ] Check List
- Bullet List
1. Numbered list

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
